Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-04 analysis/paper/paper.Rmd
Add statement on analysis of statement on instructions for sharing
Add new model for sharing instructions from journal

Most journals in our discipline fail to mention the availability of the computational methods to support the article as published.
Only two journals, *Plant Pathology* and *Tropical Plant Pathology* have full instructions for authors regarding both data and code deposition in repositories for sharing with readers.
Three had no instructions at all, *Forest Pathology*, *Phytopathologia Mediterranea* and *Revista Mexicana de Fitopatología*, with the remaining 16 journals having varying levels of instruction for authors to deposit data but not code.

@@

```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals. Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Molecular Focus, (D) Five Year Impact Factor of Journal, (E) Journal Open Access Policy and (F) Year of Publication where y is the data's density and y~rep~ are ten random posterior draws. Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}

@@

load(file = here("inst/extdata/m1.Rda"))
load(file = here("inst/extdata/m2.Rda"))
load(file = here("inst/extdata/m3.Rda"))
load(file = here("inst/extdata/m4.Rda"))
load(file = here("inst/extdata/m5.Rda"))
load(file = here("inst/extdata/m6.Rda"))

pp_m1 <- pp_check(m1)
pp_m2 <- pp_check(m2)
pp_m3 <- pp_check(m3)
pp_m4 <- pp_check(m4)
pp_m5 <- pp_check(m5)
pp_m6 <- pp_check(m6)

# put them all together
p <- (pp_m1 | pp_m2) / (pp_m3 | pp_m4) / (pp_m5 | pp_m6)

>>>>

Most journals in our discipline fail to mention the availability of the computational methods to support the article as published.
Only two journals, *Plant Pathology* and *Tropical Plant Pathology* have full instructions for authors regarding both data and code deposition in repositories for sharing with readers.
Three had no instructions at all, *Forest Pathology*, *Phytopathologia Mediterranea* and *Revista Mexicana de Fitopatología*, with the remaining 16 journals having varying levels of instruction for authors to deposit data but not code.
While the analysis did not detect an effect of the journals' instructions for sharing or depositing data and or code, the more detailed the instructions, the higher the article scored.

@@

```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualisations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals. Six factors were evaluated, (A) Publication (Journal Title), (B) Article Class, (C) Molecular Focus, (D) Five Year Impact Factor of Journal, (E) Journal Open Access Policy, (F) Year of Publication and (G) the Journals' Reproducibility Instructions where y is the data's density and y~rep~ are ten random posterior draws. Model fitnesses were found to be good for all models and no effects of any of the factors were observed on the reproducibility score.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}

@@

load(file = here("inst/extdata/m_e.Rda"))
load(file = here("inst/extdata/m_f.Rda"))
load(file = here("inst/extdata/m_g.Rda"))
load(file = here("inst/extdata/m_h.Rda"))
load(file = here("inst/extdata/m_i.Rda"))
load(file = here("inst/extdata/m_j.Rda"))
load(file = here("inst/extdata/m_k.Rda"))

pp_m_e <- pp_check(m_e)
pp_m_f <- pp_check(m_f)
pp_m_g <- pp_check(m_g)
pp_m_h <- pp_check(m_h)
pp_m_i <- pp_check(m_i)
pp_m_j <- pp_check(m_j)
pp_m_k <- pp_check(m_k)

# put them all together
p <- (pp_m_e | pp_m_f) / (pp_m_g | pp_m_h) / (pp_m_i | pp_m_j) / pp_m_k
